Standartox: A tool to derive exposure endpoints from chemical test results

### 2019-10-18 article/00_article.tex
Updates from Overleaf

\author{Andreas Scharm{\"u}ller\textsuperscript{1{*}},
        Verena Schreiner\textsuperscript{1},
        Ralf B. Sch{\"a}fer\textsuperscript{1}}

@@

\pagebreak
\section*{Supplement}
\subsection*{R-package list} %% TODO put in appropriate list
\input{article/supplement/r_package_list.tex}
\pagebreak

\subsection*{Data base tables}
\input{article/supplement/data_base_tables.tex}

>>>>

\author{Andreas Scharm{\"u}ller\textsuperscript{1{*}},
        Verena C. Schreiner\textsuperscript{1},
        Ralf B. Sch{\"a}fer\textsuperscript{1}}

@@

\subsubsection*{Future of the project}
Since new versions of the EPA ECOTOX data base are published on a quarterly basis the data acquisition process is automated and new versions of the Standartox are scheduled to be released regularly.

\pagebreak
\section*{Supplement}
\subsection*{R-package list} %% TODO put in appropriate list
\label{list:r-packages}
%% TODO how to refernce this?
\input{article/tables/r_package_list.tex}
\pagebreak

\subsection*{Data base tables}
\input{article/tables/data_base_tables.tex}

\subsection*{Application parameters}
\input{article/tables/app_parameters.tex}
